mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-01-25 thesis/thesis.tex
update

\section{Conclusion}
\label{sec:Conclusion}

%&=& &=& &=& 
% Reference
%&=& &=& &=& 
\bibliography{ref.bib}

>>>>

\section{Conclusion}
\label{sec:Conclusion}
This paper has presented the mruby bytecode loader using Bluetooth in multi-VM on mruby on TECS.
The proposed framework provides developers the efficient development without disconnecting a SD card and restarting an OS.
Furthermore, the proposed multitasking can be use more easily than the current mruby on TECS.
In the evaluation, experimental results of the mruby bytecode loader and proposed multitasking shows their advantages.
The proposed multitasking is compared with singletasking and co-routine.

%%%%%%%%%%%%%
% Reference %
%%%%%%%%%%%%%
\bibliography{ref.bib}
